Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-19 ms.tex
blackbody fit

Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$). However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features. We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.

@@

@@

\section{Retrieval of Atmospheric Composition and Thermal Structure}
\label{sec:composition}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

@@

\subsection{Dayside}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is in tension with the model at FIXME $\sigma$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

@@

\subsection{Other Orbital Phases}
We also modeled the

@@

\section{Comparison with GCMs}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC

@@

\section{Comparison of T/P Profiles}

>>>>

@@

%\section{Analysis}
%In this section we describe the interpretation of the data using simple blackbody models, a 1-D grid-based retrieval, and 3-D general circulation models (GCMs).

@@

\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
To interpret the phase-resolved spectra, we performed two model fits. First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to evaluate the atmospheric composition and thermal structure.

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provide a useful first evaluation of the atmospheric properties. The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7, \mathrm{and} 0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For most of the eastern hemisphere to just past the substellar point (phases $0.2 - 0.6$), the \Spitzer\ eclipse depths are larger than predicted for the best fit blackbody, suggesting the presence of an emission feature. On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences hint at changing thermal structure with longitude in the atmosphere.

We also fit blackbody models to the WFC3 data only, and found that they provide an excellent fit at all phases except the dayside. The $\chi^2_\nu$ values range from 0.5 to 1.4, with a median of 0.9. On the other hand, the dayside spectrum is inconsistent with a blackbody ($chi^2_\nu$ = 5.0). (FIXME: what features are there?).  The dayside spectrum has higher signal-to-noise than the other phases thanks to the two secondary eclipse observations from \citep{cartier17}, so it is not surprising that a more complex model is required.  In Table\,\ref{tab:depths} we report the best fit temperatures for the WFC3 data blackbody fits.

%Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$). However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features. We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.

\subsection{Grid-Based Retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

@@

\subsubsection{Dayside}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is in tension with the model at FIXME $\sigma$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

@@

\subsubsection{Other Orbital Phases}
We also fit the nightside spectrum with the grid-based retrieval.

@@

\subsection{Comparison with GCMs}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC

@@
